---
title: "Markdown & knitr"
output: html_document
---

```{r setup, include=FALSE}

library(doBy)
library(timeDate)
library(dplyr)

library(datasets)
library(lattice)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE )
```


1.Code for reading in the dataset and/or processing the data
& 2. Histogram of the total number of steps taken each day
```{r histG, echo=TRUE}
activity <- read.csv("activity.csv", header=T)

act <- subset(activity, select=c("date","steps"))
grp <- group_by(act, date)
step <- summarise(grp, day_step=sum(steps))

hist(step$day_step, breaks=20,xlab="No. Steps Taken",main="Histogram Total Number of Steps Taken each Day")
rug(step$day_step)  
```

3. Mean and median number of steps taken each day
```{r, MeanMedian}
step[is.na(step)] <- 0

mean(step$day_step)

median (step$day_step)
```


4. Time series plot of the average number of steps taken



```{r AverageNoSteps, echo=TRUE}

mean_step <- summarise(grp, steps=mean(steps))
xyplot(steps~date, mean_step)


```

5. The 5-minute interval that, on average, contains the maximum number of steps

```{r maxInt, echo=TRUE}
activity[is.na(activity)] <- 0

five <- group_by (activity, interval)
f <- summarise(five, step=mean(steps))
head(arrange(f, desc(step)),1)$interval
# head(arrange(f, desc(step)),1)$step # no. steps
```


6.Code to describe and show a strategy for imputing missing data
```{r impute}
activity[is.na(activity)] <- 0

```
7.Histogram of the total number of steps taken each day after missing values are imputed
```{r ImputedHistogram, echo=TRUE}

act <- subset(activity, select=c("date","steps"))


grp <- group_by(act, date)
step <- summarise(grp, day_step=sum(steps))


hist(step$day_step, breaks=20,xlab="No. Steps Taken",main="Histogram Total Number of Steps Taken each Day")
rug(step$day_step) 


```

8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r WeekDayEnd}
wk <- activity
wk$type <- isWeekday(wk$date)

wk_wk <- subset (wk, type=="TRUE")
wk_wk <- group_by(wk_wk, interval)
wk_wk <- summarise (wk_wk, steps=mean(steps))
wk_wk$day_type <- "WeekDay"

wk_end <- subset (wk, type=="FALSE")
wk_end <- group_by(wk_end, interval)
wk_end <- summarise (wk_end, steps=mean(steps))
wk_end$day_type <- "WeekEnd"


five <- arrange(rbind(wk_wk,wk_end),interval,day_type)
qplot(interval, steps, data=five, color=day_type, geom = c( "point","smooth"))

```


